Generalized Algebraic Data Types in Haskell

### 2013-06-16 gadt.tex
Wibble
Signed-off-by: Edward Z. Yang <ezyang@mit.edu>

>>>>

At this point, we have specified all cases of the \verb|leftBalance| function (note that the case of one regular node and one leaf node is not valid, because these nodes must have different black heights; so, we do not need to take care of this case). The complete source code of this example is in Appendix C.

To sum up, we have implemented and verified the insertion operation on red-black trees. By using GADTs to express invariants for this data type, we guarantee that the tree is balanced and that searching in such tree will take $O (\log n)$ time (where $n$ is total number of elements in the tree).
